---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# readstatsnz

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/MattCowgill/readstatsnz/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/MattCowgill/readstatsnz/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of {readstatsnz} is to make it easy to download and import data from StatsNZ into R.

The package enables easy access to [the CSVs listed on this page](https://www.stats.govt.nz/large-datasets/csv-files-for-download).

## Installation

You can install the development version of readstatsnz from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("MattCowgill/readstatsnz")
```

## Example

The package enables easy access to [the CSVs listed on this page](https://www.stats.govt.nz/large-datasets/csv-files-for-download).

Some StatsNZ files are simple CSVs, which can be loaded like this:
```{r example}
library(readstatsnz)

read_statsnz("national-labour-force-projections")


```

Some are ZIP files, in which case you need to supply a `subname` argument:
```{r example-2}
read_statsnz("labour-market-statistics", subname = "lci")

```


To see the available files, use:
```{r}
show_available_csvs()
```

## Lifecycle

This package is [experimental](https://lifecycle.r-lib.org/articles/stages.html#experimental). The StatsNZ website may, at any time, change in such a way that the package stops working. The package is in an early stage of development, so functions (including function names and/or arguments) may change.

## Roadmap 

In future, this package could house functions to query the StatsNZ API. I'd welcome contributions. Please open an issue before commencing.

## Disclaimer

This package is provided as-is. All data is provided under the terms set out on the StatsNZ website. This package is not in any way affiliated with or endorsed by StatsNZ.
